# Custom Markdown CSS Demo Report
`r format(Sys.Date(), "%b %d %Y")`

## Introduction

This template outlines aesthetics of [markdown_custom.css](https://github.com/malnirav/RdataObjects/blob/master/markdown_custom.css) which is a gutted version of [Bootstrap CSS](http://getbootstrap.com/css/). Furthermore, I outline few tricks of using [DataTables](http://www.datatables.net) to display long tables in reproducible reports generated using [Knitr](http://yihui.name/knitr/). 

### The code
One can reconstruct this report using following files from my [github repository](https://github.com/malnirav/RdataObjects):

* Main R source file: [markdown_custom.R](https://github.com/malnirav/RdataObjects/blob/master/markdown_custom.R)

* R markdown template of this report: [markdown_custom.Rmd](https://github.com/malnirav/RdataObjects/blob/master/markdown_custom.Rmd)

* Custom CSS file: [markdown_custom.css](https://github.com/malnirav/RdataObjects/blob/master/markdown_custom.css)

## Regular Table
```{r results="asis"}
data(mtcars)
kable(mtcars, format="html", row.names=FALSE, caption="mtcars")
```

## Table with DataTables

Note: dont forget to try regex!
```{r results="asis"}
kable(mtcars, format = "html", row.names=FALSE, caption="mtcars with DataTables",
      table.attr="id=\"datTable\"")
```